---
title: "Repeated Measures ANOVA"
output: pdf_document
params:
  descr: NA
  levene: NA
  anova: NA
  n2: NA
  emo: NA
  em1: NA
  em1_tests: NA
  em2: NA
  em2_tests: NA
  em3: NA
  em3_tests: NA
  em4: NA
  em4_tests: NA
  posthoc: NA
  plot: NA
  se: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(ft.tabcolsep=0, ft.latex.float = "none")
library(shiny)
library(dplyr)
library(knitr)
library(rempsyc)
library(flextable)
set_flextable_defaults(fonts_ignore = TRUE)
```

## Repeated Measures ANOVA

### Descriptives
```{r, results='asis'}
for(x in params$descr) print(kable(x))
```

### Levene's Test for Homogeneity of Variances
```{r}
kable(params$levene)
```


### Analysis of Variance Table
```{r}
summary(params$anova)
```

### Effect Sizes
```{r}
kable(params$n2)
```

### Estimated Marginal Means
#### Overall
```{r}
params$emo
```
#### Within Subjects Factor
```{r}
params$em1
```
```{r}
params$em1_tests
```
#### Between Subjects Factor
```{r}
params$em2
```
```{r}
params$em2_tests
```
#### Interaction
###### Pairwise Comparisons
```{r}
params$em3
```
###### Multivariate Tests
```{r}
params$em3_tests
```
###### Pairwise Comparisons
```{r}
params$em4
```
###### Univariate or Multivariate Tests
```{r}
params$em4_tests
```

### Pairwise Comparisons
```{r}
params$posthoc
```

### Plots
```{r}
params$plot
```

### Test for Simple Effects
```{r}
params$se
```